---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(BCor)
```

# R package BCor

## Overview

<!-- badges: start -->
<!-- badges: end -->

This package accompanies the paper _Measuring Dependence between Events_ by Marc-Oliver Pohle, Timo Dimitriadis and Jan-Lukas Wermuth.

It provides functions which compute estimators for correlation coefficients that are specific to $2 \times 2$ contingency tables. Additionally, the functions _YuleQ_, _Cole_ and _Phi_ yield the lower and upper bounds of the respective confidence intervals. Furthermore, we offer the corresponding inverses, i.e. functions that compute the underlying $2 \times 2$ contingency table given the value of the dependence measure and the marginal frequencies.

## Installation

To install the package from GitHub and load it, run the following `R` code:

``` r
install.packages("devtools")
library(devtools)
install_github("jan-lukas-wermuth/BCor")
library(BCor)
```

## Example

We provide a simple example illustrating the use of correlation coefficients for $2 \times 2$ contingency tables as well as their inverses. Confidence intervals are only included for Phi, Cole and Yule's Q.

```{r}
# matrix with x[1,1] = 10, x[2,1] = 20, x[1,2] = 30, x[2,2] = 5
x <- matrix(c(10, 20, 30, 5), ncol = 2) 

BCor::Phi(x)
BCor::Cole(x)
BCor::YuleQ(x)
BCor::YuleQ(x, g = 0.5)
BCor::Tetrachoric(x)
BCor::Oddsratio(x)

C <- 0.5
Q <- 0.5

# a 4 x 1 vector of marginals c(R1, R2, C1, C2)
m <- c(10, 40, 20, 30) 

BCor::Cole.inv(C, m)
BCor::YuleQ.inv(Q, m)
```
