---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(BCor)
```

# R package BCor

## Overview

<!-- badges: start -->
<!-- badges: end -->

This package accompanies the paper _Measuring Dependence between Events_ by Marc-Oliver Pohle, Timo Dimitriadis and Jan-Lukas Wermuth.

It provides functions which compute estimators for correlation coefficients that are specific to $2 \times 2$ contingency tables and fulfill the characteristic of attainability, i.e. that attain the value 1 for perfectly positively dependent (comonotonic) Bernoulli distributions and -1 for perfectly negatively dependent (countermonotonic) Bernoulli distributions. Additionally, we offer the corresponding inverses, i.e. functions that compute the underlying $2 \times 2$ contingency table given the value of the dependence measure and the marginal frequencies.

## Installation

To install the package from GitHub and load it, run the following `R` code:

``` r
install.packages("devtools")
library(devtools)
install_github("jan-lukas-wermuth/BCor")
library(BCor)
```

## Example

We provide a simple example illustrating the use of attainable correlations for $2 \times 2$ contingency tables as well as their inverses.

```{r}
x <- matrix(c(10, 20, 30, 5), ncol = 2)

Cole(x)
YuleQ(x)
Tetrachoric(x)

C <- 0.5
Q <- 0.5
m <- c(10, 40, 20, 30)

Cole.inv(C, m)
YuleQ.inv(Q, m)
```
